### 2017-11-21 manuscript.rmd
fixed species misnamings from sp\s to sp

#Load data
read.csv('character_coding/main_characters.csv', header = T, sep = ',') -> cdata
rownames(cdata) = cdata$Species

>>>>

#Load data
read.csv('character_coding/main_characters.csv', header = T, sep = ',') -> cdata
cdata$Species = str_replace_all(cdata$Species, "sp ", "sp")
rownames(cdata) = cdata$Species
